\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-15 manuscript.Rnw
Some text updates

This model can be simulated using any of the model types described in Section~\ref{sec:model-taxonomy}. We demonstrate use of all three below, starting with the iCTSTM.

@@

Since we did not fit a survival regression model containing both the absolute and relative treatment effects, we must construct the survival parameter object manually. We obtain the parameters of the fitted Weibull regression models with the generic function \code{create_params()}, and then manually add the relative treatment effects to the coefficients for the scale parameters. (Note that if we had not fit a model for SOC, the survival parameter objects could have still been constructed with \code{params_surv()}.)

@@

A number of extensions of the current version of \pkg{hesim} would be helpful. First, we plan to extend the individual-level simulation so that users can update input data during the simulation as a function of time elapsed and/or the health states transitioned to. This would allow potentially time-varying variables such as age to update each time a patient transitions to a new state. Second, we would like to add more examples to ensure that \pkg{hesim} is fit for purpose for a wide range of applications in health economics. Third, more complex models of utility \citep{kharroubi2007modelling, hernandez2013relationship} and costs \citep{nixon2005methods} could help better capture heterogeneity in preferences and spending. Fourth, it would be useful to add functionality that automatically creates tunnel states for users in cDTSTMs. Finally, a larger aspiration is to provide support for parameterization via NMA, particularly for estimation of relative treatment effects in survival (e.g., for PSMs) and multi-state models. However, since existing \proglang{R} packages are lacking in this area, this could involve creation of a separate NMA package and a new dependency for \pkg{hesim}.

>>>>

This model can be simulated using any of the model types described in Section~\ref{sec:model-taxonomy}. We demonstrate use of all three below, noting how the type of model employed should depend on the available data. We begin with the richest dataset in Section~\ref{sec:ictstm-example} and show how a flexible iCTSTM can be parameterized when continuously observed patient-level multi-state data is available. The next two sections then show how models can be developed when the data is more limited. Section~\ref{sec:psm-example} uses a PSM in a case where PFS and OS are available but multi-state data is not, and Section~\ref{sec:cdtstm-example} develops a cDTSTM in a setting where multi-state data is available but it is not continuously observed. For the sake of illustration, in both Sections~\ref{sec:psm-example} and ~\ref{sec:cdtstm-example}, patient-level data is available for the SOC, but not for estimation of relative treatment effects.

@@

Since we did not fit a survival regression model containing both the baseline risk and relative treatment effects, the survival parameter object must be constructed manually. We obtain the parameters of the fitted Weibull regression models with the generic function \code{create_params()}, and then manually add the relative treatment effects to the coefficients for the scale parameters. (Note that if we had not fit a model for SOC, the survival parameter objects could have still been constructed with \code{params_surv()}.)

The parameters for SOC are drawn by bootstrapping. Although this better accounts for the correlation between PFS and OS, it is slower than drawing the parameters from a multivariate normal distribution (as employed in Section~\ref{sec:ictstm-example}) because the survival models are refit for each PSA sample. We use the \code{max_errors} argument to allow for errors during some of the bootstrap replications (e.g., if a model fails to converge).

@@

A number of extensions of the current version of \pkg{hesim} would be helpful. First, we plan to extend the individual-level simulation so that users can update input data during the simulation as a function of time elapsed and/or the health states transitioned to. This would allow potentially time-varying variables such as age to update each time a patient transitions to a new state. Second, we would like to add more examples to ensure that \pkg{hesim} is fit for purpose for a wide range of applications in health economics. Third, more complex models of utility \citep{kharroubi2007modelling, hernandez2013relationship} and costs \citep{nixon2005methods} could help better capture heterogeneity in preferences and spending. Fourth, it would be useful to add functionality that automatically creates tunnel states for users in cDTSTMs. Fifth, equity considerations could be incorporated by adding support for distributional CEA \citep{asaria2015distributional, asaria2016distributional, cookson2017using}. Finally, a larger aspiration is to provide support for parameterization via NMA, particularly for estimation of relative treatment effects in survival (e.g., for PSMs) and multi-state models. However, since existing \proglang{R} packages are lacking in this area, this could involve creation of a separate NMA package and a new dependency for \pkg{hesim}.
